% !TeX root = ../phd-1st-year-presentation.tex
% !TeX encoding = UTF-8
% !TeX spellcheck = en_GB

\section{A hybrid technique for MRP transient analysis}
  \begin{frame}{A hybrid technique for MRP transient analysis}
    Transient analysis of Markov Regenerative Processes (MRP)\\
    employing different techniques for different epochs
    
    \vspace{1em}
    The basics:
    \begin{itemize}
      \item Exact techniques require specific conditions to be met
      \begin{itemize}
        \item different techniques require different conditions
      \end{itemize}
      \item Kernel rows of different epochs can be evaluated independently
    \end{itemize}
    
    \vspace{1em}
    The idea:
    \begin{itemize}
      \item Evaluate each kernel row with a different technique
      \begin{itemize}
        \item corresponding to the condition enabled in that epoch
        \item eventually with an approximate technique, if no conditions are met
      \end{itemize}
      \item Compute transient probabilities with Markov Renewal Equations
    \end{itemize}
  \end{frame}
  
  \begin{frame}{Analysis under enabling restriction\footnote{German, R., Logothetis, D., \& Trivedi, K. S. (1995, October). Transient analysis of Markov regenerative stochastic Petri nets: A comparison of approaches. In Petri Nets and Performance Models, 1995., Proceedings of the Sixth International Workshop on (pp. 103-112). IEEE.}}
    \textbf{Enabling restriction}
    \begin{itemize}
      \item at most one GEN enabled in each state
    \end{itemize}
    
    \vspace{1em}
    \begin{center}\scalebox{0.8}{\input{img/pn_enabling_restriction}}\end{center}
  \end{frame}
  
  \begin{frame}{Analysis with stochastic state classes\footnote{Horváth, A., Paolieri, M., Ridi, L., \& Vicario, E. (2012). Transient analysis of non-Markovian models using stochastic state classes. Performance Evaluation, 69(7), 315-335.}}
    \textbf{Bounded regeneration restriction}
    \begin{itemize}
      \item a regeneration is always reached within a bounded number of events
      \item i.e. there are no cycles without regenerations
    \end{itemize}
    
    \vspace{1em}
    \begin{center}\scalebox{0.8}{\input{img/pn_bounded_regeneration}}\end{center}
  \end{frame}
  
  \begin{frame}{Approximate analysis with stochastic state classes}
    \textbf{No restriction}
    \begin{itemize}
      \item usable when no conditions are met
    \end{itemize}
    
     \vspace{1em}
    Based on analysis with stochastic state classes
    \begin{itemize}
      \item truncated after enough precision is met
    \end{itemize}
    
    \vspace{1em}
    \begin{center}\scalebox{0.8}{\input{img/pn_no_restriction}}\end{center}
  \end{frame}
